---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ooklaOpenDataR

<!-- badges: start -->
<!-- badges: end -->

The goal of ooklaOpenDataR is to make it easier to access data from Ookla's [open data program](https://registry.opendata.aws/speedtest-global-performance/). This dataset provides global fixed broadband and mobile (cellular) network performance metrics in zoom level 16 [web Mercator tiles](https://en.wikipedia.org/wiki/Tiled_web_map) (approximately 610.8 meters by 610.8 meters at the equator). The tiles are updated quarterly. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("teamookla/ooklaOpenDataR")
```
## Examples

This is how you can get the global dataset for mobile network data in Q2 2020:

```{r example, eval = FALSE}
library(ooklaOpenDataR)

mobile_q2 <- get_performance_tiles(service = "mobile", quarter = 2, year = 2020)
```

Or you can get the fixed broadband data for the same quarter as an `sf` data frame with the `sf` argument.

```{r fixed_example, eval = FALSE}
fixed_q2_sf <- get_performance_tiles(service = "mobile", quarter = 2, year = 2020)
```

The package vignettes demonstrate how to filter the tiles to a particular area of interest using the `filter_by_quadkey()` function. 

## License

The dataset is licensed under the [Creative Commons license for non-commerical use](https://creativecommons.org/licenses/by-nc-sa/4.0/).

**Recommended citation**

Speedtest® by Ookla® Global Fixed and Mobile Network Performance Maps. Based on analysis by Ookla of Speedtest Intelligence® data for [DATA TIME PERIOD]. Provided by Ookla and accessed [DAY MONTH YEAR]. Ookla trademarks used under license and reprinted with permission.
